Analysis of NLA17 Dissolved Gas Indicator

### 2021-09-22 scripts/dgIndicatorAnalysis.Rmd
syncing up after ASLO 2021 slide preparation

plot(model)
text(model)
```

>>>>

plot(model)
text(model)
```
# ASLO 2021

## Site Map
```{r}
# Load data
 load(paste0(localPath,
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2021-02-01.RData"))

# To enable mapping the dataframe will be converted to a 'simple features' (sf) object.
# Define coordinates
coords <- data.frame(longitude = dg$map.lon.dd, latitude = dg$map.lat.dd)

# Load state boundaries
states <- USAboundaries::us_states() %>%
  dplyr::filter(!state_name %in% c("Alaska", "District of Columbia", "Hawaii", "Puerto Rico")) %>%
  st_transform(5070) # convert to CONUS Albers

ggplot() +
  geom_sf(data = ecoR, color = NA, aes(fill = WSA9_NAME)) +
  geom_sf(data = dg.sf) +
  geom_sf(data = states, fill = NA, color = "white", size = 0.1) +
  theme_void() +
  theme(legend.title = element_blank())

ggsave("output/figures/siteMap.tiff")

## Population Data

```{r}
# about 15 minutes to load first time
# 6/7/21 <2 minutes
Sys.time()
load(paste0(localPath, "\\Environmental Protection Agency (EPA)\\ORD NLA17 Dissolved Gas - Documents\\inputData\\all_predictions.rda"))
Sys.time()
```

## Explore structure of all_predictions object
```{r}
head(all_predictions)
```
.row uniquely identifies each waterbody.  There are `r all_predictions %>% distinct(.row) %>% nrow()` waterbodies in the sample frame.  `.draw` reflects the simulation number for each waterbody. I think this is a 'draw from the posterior distribution'.  The data contains `r all_predictions %>% distinct(.draw) %>% nrow()` draws for each waterbody.

The `size_cat` variable largely uses the NLA size category definitions.  This may not be the best for showing N2O fluxes by lake size bins, however.  The >50 ha (0.5km2) has most of the surface area

```{r}
# total area by size_cat bar chart
all_predictions %>%
  filter(.draw == 1) %>%
  group_by(WSA9, size_cat) %>%
  summarise(tot_area = sum(area_ha)) %>%
  ggplot(aes(x=size_cat, y=tot_area)) +
  geom_bar(stat = "identity") +
  facet_wrap(~WSA9)

Lets create a new size category with more even surface area distributions.

```{r}
# 11 minutes on VM!
all_predictions <- all_predictions %>%
  #filter(.draw == 1) %>% # testing
  mutate(area_km2 = area_ha / 100, # this works
         size_cat2 = ifelse(area_km2 < 0.1,
                            "<0.1",
                            ifelse(area_km2 >= 0.1 & area_km2 < 1,
                                   "0.1 - 1",
                                   ifelse(area_km2 >=1 & area_km2 <10,
                                          "0.1 - 1",
                                          ifelse(area_km2 >=10 & area_km2 <100,
                                                 "10 - 100",
                                                 ifelse(area_km2 >=100, 
                                                        ">100",
                                                        NA))))),
         size_cat2 = factor(size_cat2, ordered = TRUE, 
                            levels = c("<0.1", "0.1 - 1", "1 - 10", "10 - 100", ">100"))) %>%
  select(-area_km2)

# total area by size_cat2 bar chart
all_predictions %>%
  filter(.draw == 1) %>%
  group_by(WSA9, size_cat2) %>%
  summarise(tot_area = sum(area_ha)) %>%
  ggplot(aes(x=size_cat2, y=tot_area)) +
  geom_bar(stat = "identity") +
  facet_wrap(~WSA9)

## Reorder WSA9
Reorder WSA9 to correspond with order of first micromap produced below, which is ordered by extent of N2O saturation.
```{r}
all_predictions <- all_predictions %>%
  mutate(WSA9 = factor(WSA9,
                       levels = c("NPL", "TPL", "UMW", 
                                  "CPL", "SPL", "SAP",
                                  "XER", "NAP", "WMT"),
                       labels = c("Northern Plains", "Temperate Plains",
                                  "Upper Midwest", "Coastal Plains", "Southern Plains", "Southern Appalachians", "Xeric", "Northern Appalachians", "Western Mountains")))

## N2O saturation ratio: continuous variable
N2O saturation ratio in the sample data has a long right tail, with a maximum value of ~30.  The distribution of the values predicted to the population also has a long right tail, but features more extreme values (>600).
```{r}
# PLOT N2O SAT RATIO BY WSA9

# point and linerange
all_predictions %>%
  group_by(WSA9, .draw) %>%
  #group_by(.draw) %>%
  summarise( mean_sat = mean(preds_sat)) %>%
  summarise( estimate = round(median(mean_sat), 3),
    LCL = round(quantile(mean_sat, probs = 0.025), 3),
    UCL = round(quantile(mean_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  #mutate(type = "MR") %>%
  select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = ecoregion, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL)) +
  geom_hline(yintercept = 1, color='blue') +
  ylab("mean N2O saturation ratio") +
  coord_flip() + 
  theme_bw()

# density plots of predicted distribution
# using xlim to zoom in on values close to 1
p <- all_predictions %>%
  filter(.draw %in% 1:10) %>% # subset for practice
  #mutate(ecoregion = factor(WSA9)) %>%
  #mutate(ecoregion = fct_reorder(ecoregion, preds_sat)) %>%
  ggplot( aes( x = preds_sat, group = .draw, color = .draw ) ) +
  geom_density(show.legend = FALSE) +
  geom_vline(xintercept = 1, color = "red") +
  xlab(expression(N[2]*O~saturation~ratio)) +
  xlim(0,5) + # data range is 0-600, but sample max is 30
  facet_wrap(~WSA9) +
  theme_bw()

# this bit fills strip with same colors used in micromap (see below)
#https://stackoverflow.com/questions/19440069/ggplot2-facet-wrap-strip-color-based-on-variable-in-data-set
g <- ggplot_gtable(ggplot_build(p))
stripr <- which(grepl('strip-t', g$layout$name)) # need strip-t, not strip-r
fills <- rep(brewer.pal(5, "Spectral")[c(1,3,5)], 3) # these are the 3 colors used in micromap
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
grid::grid.draw(g)

ggsave("output/figures/n2oSatDensitySmallRange.tiff", g)

summary(dg$n2o.sat.ratio) # max value in sample is 33

# rplot, but show full x-axis range
# include RUG to better show extreme values
p <- all_predictions %>%
  filter(.draw == 1) %>% # need only one draw, otherwise RUG is misleading
  #mutate(ecoregion = factor(WSA9)) %>%
  #mutate(ecoregion = fct_reorder(ecoregion, preds_sat)) %>%
  ggplot( aes( x = preds_sat ) ) +
  geom_density(color = "blue") +
  geom_vline(xintercept = 1, color = "red") +
  geom_rug() +
  xlab(expression(N[2]*O~saturation~ratio)) +
  #xlim(0,35) + # data range is 0-600, but sample max is 30
  facet_wrap(~WSA9, scales = "free") +
  theme_bw()

# this bit fills strip with same colors used in micromap (see below)
#https://stackoverflow.com/questions/19440069/ggplot2-facet-wrap-strip-color-based-on-variable-in-data-set
g <- ggplot_gtable(ggplot_build(p))
stripr <- which(grepl('strip-t', g$layout$name)) # need strip-t, not strip-r
fills <- rep(brewer.pal(5, "Spectral")[c(1,3,5)], 3) # these are the 3 colors used in micromap
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
grid::grid.draw(g)

ggsave("output/figures/n2oSatDensityFullRange.tiff", g)

# Take a peak at values >40 in predictions
all_predictions %>%
    filter(preds_sat > 40, .draw == 1) %>% # look at one draw
  {table(.$WSA9)} # >40 is uncommon outside of CPL

# # density plots of observed distribution
# huge right tail
dg %>%
  mutate(ecoregion = factor(ag.eco9.nm)) %>%
  mutate(ecoregion = fct_reorder(ecoregion, n2o.sat.ratio)) %>%
  ggplot( aes( x = n2o.sat.ratio ) ) +
  geom_density() +
  xlab("mean N2O saturation ratio") +
  facet_wrap(~ecoregion) +
  theme_bw()

## N2O saturation ratio: extent estimate
```{r}
# EXTENT OF WATERBODIES FUNCTIONING AS SINKS BY ECOREGION

# density plot
all_predictions %>%
  group_by(WSA9, .draw) %>%
  # below summarise generates 500 proportions per WSA
  summarise(prop_sat = sum(preds_sat < 1) / length(unique(.row))) %>%
  ggplot(aes(x=prop_sat)) + 
  geom_density() +
  facet_wrap(~WSA9) +
  xlab("Proportion of waterbodies functioning as N2O sinks") +
  theme_bw()
ggsave("output/figures/extentDensityPlot.tiff")

# point and line plot
all_predictions %>%
  group_by(WSA9, .draw) %>%
  summarise(prop_sat = sum(preds_sat < 1) / length(.row)) %>% # Roy had length(unique(.row)) here, but the unique isn't necessary.  this object is grouped by WSA9
  summarise(estimate = round(median(prop_sat), 3),
    LCL = round(quantile(prop_sat, probs = 0.025), 3),
    UCL = round(quantile(prop_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = ecoregion, y = estimate ) ) +
  geom_point() +
  geom_linerange( aes( ymin = LCL, ymax = UCL )) +
  ylab("Proportion of waterbodies functioning as N2O sinks") +
  coord_flip() + 
  theme_bw()
ggsave("output/figures/extentPointLinerange.tiff")

# bar and line plot
all_predictions %>%
  group_by(WSA9, .draw) %>%
  summarise(prop_sat = sum(preds_sat < 1) / length(.row)) %>% # Roy had length(unique(.row)) here, but the unique isn't necessary.  this object is grouped by WSA9
  summarise(estimate = round(median(prop_sat), 3),
    LCL = round(quantile(prop_sat, probs = 0.025), 3),
    UCL = round(quantile(prop_sat, probs = 0.975), 3)) %>% 
  mutate(ecoregion = factor(WSA9)) %>%
  select(ecoregion, estimate, LCL, UCL) %>%
  mutate(ecoregion = fct_reorder(ecoregion, estimate)) %>%
  ggplot( aes( x = ecoregion, y = estimate ) ) +
  geom_bar(stat = "identity", aes(fill = ecoregion)) +
  geom_linerange( aes( ymin = LCL, ymax = UCL )) +
  ylab("Proportion of waterbodies functioning as N2O sinks") +
  coord_flip() + 
  theme_bw()  
ggsave("output/figures/extentBar.tiff")
```

## N2O emission rate and flux
### Calculations
Roy predicted N2O equilibrium and concentration to the population.  I used ERA5 to calculate mean wind speed during the index period for each lake in the population.  I need to match wind speed to Roy's predictions.  Waterbodies in Roy's predictions are identified by '.row'.  There are `r all_predictions %>% distinct(.row) %>% summarize(population = n()) %>% pull()` rows.

```{r}

# Read in wind data
# Mean index period wind speed was calculated on VM via 
# nlaSampleFrameWind.R.  The resulting data object was written out and read in below.
wind <- read.table(paste0(Sys.getenv("USERPROFILE"), 
                                    "/Environmental Protection Agency (EPA)/",
                                    "ORD NLA17 Dissolved Gas - Documents/",
                                    "inputData/windSampleFrame.txt"))
# print first 6 lines
wind %>% head()

# print first 6 .row values of all_predictions
all_predictions %>%
  filter(.row %in% 1:6) %>% # each row is a unique waterbody
  group_by(.row) %>%
  slice(1) # grabs first record

# Row order in wind and all_predictions is inherited from sample frame.  Thus row 1
# of wind corresponds to .row == 1 in all_predictions.  This is a sketchy way to merge
# things, but will do for now.

# add .id to wind which is simply row number
wind <- wind %>% mutate(.id = row_number())

# Merge wind and all_predictions
all_predictions.w <- full_join(all_predictions, wind, by = c(".row" = ".id")) # too much for laptop,30 seconds on VM
dim(wind) # 465897
dim(all_predictions) #232948500, 500 observations for each lake
465897*500 #232948500
dim(all_predictions.w) #wind.sampFr. good

# ESTIMATE GAS EXCHANGE RATE FOR POPULATION

# Using gas exchange model from:
# Vachon, D., and Y. T. Prairie (2013), The ecosystem size and shape 
# dependence of gas transfer velocity versus wind speed relationships in 
# lakes, Can. J. Fish. Aquat. Sci., 70(12), 1757-1764, doi:10.1139/cjfas-2013-0241.
# Table 2, model B.

# define k600 prediction function
pred.k600 <- function(ws, area) { 
  # predict k600 in cm h-1
  # ws = wind speed (m s-1)
  # area = lake area (km2)
  2.51 + (1.48 * ws) + (0.39 * ws * log10(area))
}

all_predictions.w <- all_predictions.w %>%
  mutate(k600.cm.h = pred.k600(ws = ws, area = area_ha/100), # 100ha = 1km2
         # 1000 L to m3. 44ng to 1nmol. ng->ug. ug->mg
         e.n2o.mg.m2.d = (((preds_n2o - preds_n2oeq) * 1000 * 44) / (1000 * 1000)) * 
           (k600.cm.h * (24/100)), #h->day. cm->m
         f.n2o.Mg.y = (e.n2o.mg.m2.d * 365 * (area_ha*10000)) / # day to year. ha to m2.
           (1000*1000*1000)) #mg-g, g-kg, kg-Mg

# write reduced file to disk for less computationally intensive wrangling
#all_predictions.w.small <- all_predictions.w %>% filter(.draw %in% 1:5)

#save(all_predictions.w.small,
#     file = paste0(Sys.getenv("USERPROFILE"), 
#                   "/Environmental Protection Agency (EPA)/",
#                   "ORD NLA17 Dissolved Gas - Documents/",
#                   "inputData/all_predictions_w_small.rda"))
```
### compared to literature and US GHG inventory
The distribution of N2O emission rates (mg N2O m-2 d-1) for one draw is very similar to that derived from a literature review of lake/reservoir emission rates (DelSontro et al), except for CPL which shows some exceedingly high rates.  Overall, our results look reasonable.

The total N2O flux from US lakes and reservoirs is minor compared to other anthropogenic N2O sources
```{r}
all_predictions.w %>% 
  filter(.draw == 1) %>% 
  ggplot(aes(x=e.n2o.mg.m2.d)) + 
  geom_density() +
  geom_rug() + 
  facet_wrap(~WSA9, scales = "free")

knitr::include_graphics((paste0(Sys.getenv("USERPROFILE"), 
                                    "/Environmental Protection Agency (EPA)/",
                                    "ORD NLA17 Dissolved Gas - Documents/",
                                    "EDA/en2oLiterature.tiff")))

## Comparison to US GHG inventory
# top sources from inventory report in kt / year
n2o <- data.frame(kt = c(1156,88,84,66,60,34,18,14,7),
                     source = c("Agricultural Soil Management",
                                "Wastewater Treatment",
                                "Stationary Combustion",
                                "Manure Management",
                                "Mobile Combustion",
                                "Nitric Acid Production",
                                "Adipid Acid Production",
                                "N2O from Product Uses",
                                "Composting"))

n2o <- n2o %>% mutate(Mg = (kt * 1000 * 1000) / 1000,  # 1000 metric tons in a kt, 1000 kg in a metric ton, 1000 kg in a Mg
                      Gg = Mg / 1000)

# National scale number for lakess/reservoirs (this is is Gg)
national.lakes <- all_predictions.w %>% 
  group_by(.draw) %>% 
  summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  summarise(Gg = round(mean(total.n2o), 3) / 1000, # divide by 1000 for Mg to Gg
            Gg_LCL = round(quantile(total.n2o, probs = 0.025), 3) / 1000, # divide by 1000 for Mg to Gg
            Gg_UCL = round(quantile(total.n2o, probs = 0.975), 3) / 1000) %>% # divide by 1000 for Mg to Gg
  mutate(source = "Lakes and Reservoirs")

# Merge lakes and inventory category
inventory <- full_join(n2o, national.lakes)
inventory

inventory %>% mutate(source = as.factor(source),
                     source = reorder(source, Gg)) %>%
  ggplot(aes(source, Gg)) +
  geom_bar(stat = "identity", color = "orange", fill = "orange") +
  geom_errorbar(aes(x=source, ymin = Gg_LCL, ymax = Gg_UCL), width = 0.5) +
  coord_flip() +
  ylab(expression(N[2]*O~flux~(Gg~year^{-1}))) +
  theme_bw() +
  theme(axis.title.y = element_blank())
ggsave(filename = "output/figures/n2oInventory.tiff")

tiff("output/figures/n2oInventoryPie.tiff")
pie.labels <- c("Agricultural Soil Management",
                "Wastewater Treatment",
                "Stationary Combustion",
                "Manure Management",
                "Mobile Combustion",
                "Nitric Acid Production",
                NA,
                NA,
                NA,
                "Lakes and Reservoirs")
pie(inventory$Gg, labels = pie.labels, col = brewer.pal(8, "Set2"), radius = 0.6, cex = 0.9)
dev.off()

(national.lakes$Gg/sum(inventory$Gg)) * 1000 #1.6%
```

### Figures and tables
Below is the distribution of total annual fluxes from the lakes.  This is calculated as lake area * emission rate.

```{r}
# density plot with RUG for one draw
all_predictions.w %>% filter(.draw == 1) %>% ggplot(aes(x=f.n2o.Mg.y)) + geom_density() +geom_rug() + facet_wrap(~WSA9, scales = "free")

# flux vs area for one draw
all_predictions.w %>% filter(.draw == 1) %>% ggplot(aes(y=f.n2o.Mg.y, x=area_ha)) + geom_point() + facet_wrap(~WSA9, scales = "free")

# bar plot by size category and ecoregion  
all_predictions.w %>% filter(.draw == 1) %>% group_by(WSA9, size_cat2) %>% summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  ggplot(aes(x=size_cat2, y=total.n2o)) + geom_bar(stat = "identity") + facet_wrap(~WSA9, scales = "free")

# bar plot by size category with error
p <- all_predictions.w %>% 
  group_by(WSA9, .draw, size_cat2) %>% 
  summarise(total.n2o = sum(f.n2o.Mg.y)) %>% 
  group_by(WSA9, size_cat2) %>%
  summarise(post_med_fn2o = round(mean(total.n2o), 3), 
            LCL_fn2o = round(quantile(total.n2o, probs = 0.025), 3),
            UCL_fn2o = round(quantile(total.n2o, probs = 0.975), 3)) %>%
  ggplot(aes(x=size_cat2, y=post_med_fn2o)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(x=size_cat2, ymin = LCL_fn2o, ymax = UCL_fn2o)) +
    xlab(expression(Lake~Size~Bin~(km^{2}))) +
  ylab(expression(Mg~N[2]*O~year^{-1})) +
  facet_wrap(~WSA9, scales = "free") +
  theme_bw()

# this bit fills strip with same colors used in micromap (see below)
#https://stackoverflow.com/questions/19440069/ggplot2-facet-wrap-strip-color-based-on-variable-in-data-set
g <- ggplot_gtable(ggplot_build(p))
stripr <- which(grepl('strip-t', g$layout$name)) # need strip-t, not strip-r
fills <- rep(brewer.pal(5, "Spectral")[c(1,3,5)], 3) # these are the 3 colors used in micromap
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
grid::grid.draw(g)

ggsave("output/figures/n2oFluxByLakeSizeWithError.tiff", g)

# bar plot by size category without error
p <- all_predictions.w %>% 
  group_by(WSA9, .draw, size_cat2) %>% 
  # tot x size x draw
  summarise(total.n2o = sum(f.n2o.Mg.y),
            obs = n()) %>% # number of lakes per WSA x size
  group_by(WSA9, size_cat2) %>%
  summarise(post_med_fn2o = round(mean(total.n2o), 3), # across draws
            LCL_fn2o = round(quantile(total.n2o, probs = 0.025), 3),
            UCL_fn2o = round(quantile(total.n2o, probs = 0.975), 3),
            obs = mean(obs)) %>% # obs is repeated across draws.  mean gives identity
  ggplot(aes(x=size_cat2, y=post_med_fn2o)) + 
  geom_bar(stat = "identity") + 
  xlab(expression(Lake~Size~Bin~(km^{2}))) +
  ylab(expression(Mg~N[2]*O~year^{-1})) +
  #scale_x_discrete(labels = c("min to 4", "4-10", "10-20", "20-50", ">50")) +
  #geom_errorbar(aes(x=size_cat, ymin = LCL_fn2o, ymax = UCL_fn2o)) +
  facet_wrap(~WSA9, scales = "free_y") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  geom_text(aes(label = scales::comma(obs, accuracy = 1)), # comma for thousands separator, accurary for decimal points
            vjust = -0.5, size = 3) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.2)))

# this bit fills strip with same colors used in micromap (see below)
#https://stackoverflow.com/questions/19440069/ggplot2-facet-wrap-strip-color-based-on-variable-in-data-set
g <- ggplot_gtable(ggplot_build(p))
stripr <- which(grepl('strip-t', g$layout$name)) # need strip-t, not strip-r
fills <- rep(brewer.pal(5, "Spectral")[c(1,3,5)], 3) # these are the 3 colors used in micromap
k <- 1
for (i in stripr) {
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
  k <- k+1
}
grid::grid.draw(g)

ggsave("output/figures/n2oFluxByLakeSizeNoError.tiff", g)

## micromap: N2O saturation ratio continuous, extent, and emission rate
```{r}
# summarize means by WSA9 (posterior median for mean and 95% credible intervals)
# this is analogous to spsurvey "population estimates"
ecoreg_stats <- all_predictions.w %>%
  group_by(WSA9, .draw) %>%
  summarise( mean_n2o = mean(preds_n2o),
             mean_n2oeq = mean(preds_n2oeq),
             mean_sat = mean(preds_sat),
             prop_sat = sum(preds_sat < 1) / length(unique(.row)),
             mean_en2o = mean(e.n2o.mg.m2.d),
             fn2o_Mg = sum(f.n2o.Mg.y)) %>%
  summarise( post_med_n2o = round(mean(mean_n2o), 1),
             LCI_n2o = round(quantile(mean_n2o, probs = 0.025), 1),
             UCI_n2o = round(quantile(mean_n2o, probs = 0.975), 1),
             post_med_n2oeq = round(mean(mean_n2oeq), 2),
             LCI_n2oeq = round(quantile(mean_n2oeq, probs = 0.025), 2),
             UCI_n2oeq = round(quantile(mean_n2oeq, probs = 0.975), 2),
             post_med_sat = round(mean(mean_sat), 2),
             LCI_sat = round(quantile(mean_sat, probs = 0.025), 2),
             UCI_sat = round(quantile(mean_sat, probs = 0.975), 2),
             estimate = round(mean(prop_sat), 3),
             LCL = round(quantile(prop_sat, probs = 0.025), 3),
             UCL = round(quantile(prop_sat, probs = 0.975), 3),
             post_med_en2o = round(mean(mean_en2o), 3),
             LCL_en2o = round(quantile(mean_en2o, probs = 0.025), 3),
             UCL_en2o = round(quantile(mean_en2o, probs = 0.975), 3),
             post_med_fn2o = round(mean(fn2o_Mg), 3), 
             LCL_fn2o = round(quantile(fn2o_Mg, probs = 0.025), 3),
             UCL_fn2o = round(quantile(fn2o_Mg, probs = 0.975), 3),
             n = dplyr::n())

ecoreg_stats$WSA9_NAME <- as.character(ecoreg_stats$WSA9)
ecoreg_stats <- ecoreg_stats %>% select(-WSA9)
str(ecoreg_stats)

# N2O SATURATION AND UNDERSATURATION EXTENT
# Full code:  Use this to produce final linked micromaps of the variables you want
# export as pdf US letter landscape from Plots pane
# export as PNG Width 900 Height 968, maintain aspect ratio

mmplot(stat.data=ecoreg_stats,
       map.data=ecor.polys,
       panel.types=c('dot_legend', 'labels', 'dot_cl', 'dot_cl', 'map'),
       panel.data=list(
         NA,
         'WSA9_NAME',
         list('estimate', 'LCL', 'UCL'),
         list('post_med_sat', 'LCI_sat', 'UCI_sat'),
         NA),
       ord.by = 'estimate', rev.ord = TRUE, grouping=3,
       median.row=FALSE,
       map.link=c('WSA9', 'ID'),

       plot.height=5, # what does this do?
       plot.width=7, #what does this do? 
       colors=brewer.pal(5, "Spectral"), #for journal use plot.height=9, plot.width=6.8
       map.color2='lightgray',

       panel.att=list(list(1, point.type=20, point.size=2,
                           graph.border.color='white',
                           xaxis.text.display=F, xaxis.line.display=F,
                           graph.grid.major=F, 
                           panel.width = 2), # added this argument to ensure the full point is shown

                      list(2,  panel.width=2,#increased panel.width to 1.1 from .8, removed header='NARS Reporting\n Regions',
                           align='left', text.size=0.8),#increased text.size to .8 from .6

                      list(3, header= "Proportion undersaturated\n with 95% CI", 
                           graph.bgcolor='lightgray',
                           #xaxis.ticks=list(6.0, 7.0, 8.0, 9.0, 10.0),
                           #xaxis.labels=list(6.0, 7.0, 8.0, 9.0, 10.0),
                           xaxis.title='Proportion undersaturated', panel.width=2.3),

                      list(4, header="N2O Saturation\n with 95% CI", #N2O Saturation\n with 95% CI
                           graph.bgcolor='lightgray',
                           xaxis.ticks=list(0.8, 1.0, 1.2, 1.4, 1.6),
                           xaxis.labels=list(0.8, 1.0, 1.2, 1.4, 1.6),
                           xaxis.title='N2O Saturation, %',panel.width=2.3),

                      list(5, header='Light Gray Means\n Highlighted Above',
                           inactive.border.color=gray(.7), inactive.border.size=2,
                           panel.width=2)),

       print.file = "output/figures/mmapSatExtent.tiff", print.res = 300)

# N2O EMISSION AND FLUX
# Full code:  Use this to produce final linked micromaps of the variables you want
# export as pdf US letter landscape from Plots pane
# export as PNG Width 900 Height 968, maintain aspect ratio

mmplot(stat.data=ecoreg_stats,
       map.data=ecor.polys,
       panel.types=c('dot_legend', 'labels', 'dot_cl', 'dot_cl', 'map'),
       panel.data=list(
         NA,
         'WSA9_NAME',
         list('post_med_en2o', 'LCL_en2o', 'UCL_en2o'),
         list('post_med_fn2o', 'LCL_fn2o', 'UCL_fn2o'),
         NA),
       ord.by = 'post_med_en2o', rev.ord = TRUE, grouping=3,
       median.row=FALSE,
       map.link=c('WSA9', 'ID'),

       plot.height=5, # what does this do?
       plot.width=7, #what does this do? 
       colors=brewer.pal(5, "Spectral"), #for journal use plot.height=9, plot.width=6.8
       map.color2='lightgray',

       panel.att=list(list(1, point.type=20, point.size=2,
                           graph.border.color='white',
                           xaxis.text.display=F, xaxis.line.display=F,
                           graph.grid.major=F, 
                           panel.width = 2), # added this argument to ensure the full point is shown

                      list(2,  panel.width=2,
                           align='left', text.size=0.8),

                      list(3, header= "Emission rate\n with 95% CI", 
                           graph.bgcolor='lightgray',
                           #xaxis.ticks=list(6.0, 7.0, 8.0, 9.0, 10.0),
                           #xaxis.labels=list(6.0, 7.0, 8.0, 9.0, 10.0),
                           xaxis.title='Emission rate (mg m-2 d-1)', panel.width=2.3),

                      list(4, header="N2O flux\n with 95% CI", #N2O Saturation\n with 95% CI
                           graph.bgcolor='lightgray',
                           #xaxis.ticks=list(0.8, 1.0, 1.2, 1.4, 1.6),
                           #xaxis.labels=list(0.8, 1.0, 1.2, 1.4, 1.6),
                           xaxis.title="N2O flux (Mg y-1)", panel.width=2.3),

                      list(5, header='Light Gray Means\n Highlighted Above',
                           inactive.border.color=gray(.7), inactive.border.size=2,
                           panel.width=2)),

       print.file = "output/figures/mmapEmisFlux.tiff", print.res = 300)
```
